### 2022-03-10 02_paper/02_study/paper_methods.Rmd
paper method

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes"

@@

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

@@

```{r demographicstable, echo = FALSE}

@@

# changing gender female 1 = 0
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

@@

# creating new column with percentage of gender

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female" = sum(Gender),
            "M Age in years" = round(mean(Age), 0),
            "SD Age in years" = round(sd(Age), 0),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp.in years" = max(`Teaching Experience`),
           )

@@

The planned sample consists of *n* = 40 experts (teacher training completed, active in the teaching profession) and *n* = 40 novices (student teachers, first internship completed).

The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group=="Expert")` experts and

*n* = r nrow(demo.data[demo.data$Group == "Novice",]) novices.

Participants Teachers were primarily recruited through personal contacts

@@

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

>>>>

---
title             : "Through the eyes of the teacher"
shorttitle        : "Multimodal exploration of expertise differences in the perception of classroom disruptions"

@@

  Financial Support: We received funding from QualiFond to support the qualification of young academics from the University Leipzig.

@@

floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

- wie wird Störung definiert
-

@@

```{r demographicstable, echo=FALSE}

@@

# changing gender to count female gender (male = 2 --> 0)
demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")

@@

# creating new column with percentage of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Gender_Sum=n())

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
demo.data <- demo.data  %>% 
  group_by(Group) %>% 
  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = Gender_percentage,
            "M Age in years" = round(mean(Age), 0),
            "SD Age in years" = round(sd(Age), 0),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp.in years" = max(`Teaching Experience`),
           )

@@

The sample consists of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.

The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession. Novices were student teachers who have already successfully completed their first internship in a school and have gained one to four hours of teaching experience.

The subjects were primarily recruited through personal contacts, social media (facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.

The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of

The participants (98
women; 80%) had a mean age of 23.96 years (SD = 5.82; range:
18–48), and 13 of them (11%) reported to live together with
their child/children. Whereas 21 participants (17%) lived alone,
the remaining participants (n = 102; 83%) lived in a household
consisting of 2–10 persons, with the majority (n = 93)
living in a household of 2–4 persons. At baseline (July
2020), n = 10 participants (8%) reported flu-like symptoms
with one participant being in COVID-related quarantine.

@@

## Procedure
In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.

## Data analysis
All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28. Data analysis scripts
can be obtained from the authors upon request.
